---
title       : The click plot application!
subtitle    : 
author      : markist
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Application

This is a shiny application to calculate 

- mean,
- median and
- standard deviation 

from longitudinal data.

---

## The data (I)

Wind data from the aiquality data set can be seleted.

````{r, echo=FALSE}
require(graphics)
plot(airquality$Day,airquality$Wind)
plot(airquality$Day,airquality$Temp)
````


---

## The data (II)

Temperature data from the aiquality data set can be seleted as well!

````{r,echo=FALSE}
require(graphics)
plot(airquality$Day,airquality$Temp)
````

---

## Start now!

To get started:

Click into the plot:

- go to: https://markist.shinyapps.io/CourseraShinyApp/
- click on the plot
- a line where you clicked will be shown
- the calculated variable will be plotted between the clicks

- P.S: You can choose a title!




